\section{Discussion}
\label{sec:Diskussion}

\subsection{Contrast}

As can be seen in \autoref{fig:contrast} the measured contrast fit to the theoretical course.
As expected most measurement point lie below the theory. 
This is a result not perfect mirrors and filters, which all are absorbing a small amount of the light.
An unexpected result is the negative contrast at $\SI{90}{\degree}$.
A possible explanation is that the apperature is extremely sensitive and even more so at the extremes of the contrast.
In addition background light could be a source for distortion of the result.

\subsection{Glass}

It is not know form which glass the plate is made exactly, but two of the most common glass types are quartz glass $n_{q} = 1.457$\cite{Malitson:65} and soda-lime glass $n_{l} = 1.522$ \cite{RUBIN1985275},
which a measured value of $n = \SI{1.506 \pm 0.047}{}$ this results in a relative deviation of $\Delta n_q = \SI{-3.3 \pm 3.0} \,\%$ and
$\Delta n_l = \SI{1.0 \pm 3.1}\,\%$ respectively. 
So examined plate could comprehensible be soda-lime glass.
As can be seen in \autoref{fig:n_ns_p} the change in pressure is not constant. 
A near constant increase of pressure was tried to achieve by opening the valve gradually, but could have distorted the detector and as consequence the counted zero passes at the detector.

\subsection{Air}

The literature value, as given by the manual, for the refractive of dry air at $15\, \unit{\degree}$, $1\, \unit{\bar}$ and $450$ ppm $CO_{2}$ content is $n_{A} = \SI{1.00027654}{}$ \cite{Ciddor:96}.
This results in a relative deviation of  $\Delta n_{A} = \SI{0.0067 \pm 0.0028}{} \%$ with the measured value of $\overline{n} = \SI{1.000343 \pm 0.000028}{}\,$. 
It should be noted that the measured room temperature was $\SI{21.6}{\celsius}$, which is quite a bit, although not relevantly higher than the given $\SI{15}{\celsius}$.