\documentclass[12pt]{article}
\usepackage{geometry}

\parindent=0pt

\geometry{a4paper, margin=1in}

\begin{document}

% Right-aligned sender's information
\noindent
\begin{minipage}[t]{\textwidth}
\raggedleft
\textbf{Jonas Ollesch} \\
Department of Physics \\
TU Dortmund University \\
Froschlake 10 \\
44379 Dortmund \\
Email: jonas.ollesch@tu-dortmund.de \\
\end{minipage}

\vspace{1.5cm} % Adjust vertical space as needed

% Left-aligned date and recipient's information
\noindent
\textbf{Date:} \today

\vspace{0.5cm}

\noindent
\textbf{To:} \\
Prof. Dr. Johannes Albrecht \\
Department of Physics\\
TU Dortmund University \\

\vspace{1cm}

\noindent
\textbf{Subject:} Letter of Recommendation for Pascal Machnik

\vspace{1cm}

Dear Prof. Dr. Albrecht,

\vspace{.5cm}

my name is Jonas Ollesch. I am currently writing my master's thesis in the field of theoretical particle physics at TU Dortmund University.
I had the pleasure of getting to know Pascal Machnik not only in the module “Einführung in die Kern- und Elementarteilchenphysik”
but also in the modules “Höhere Mathematik IV” and “Statistical Methods of Data Analysis” during my time as a student assistant 
in the summer semester of 2024 and the winter semester of 2024/2025.
Even before meeting Pascal, I had heard of him through my colleague and friend Max Freiheit, who described him as an extraordinarily motivated and intelligent student.

In all these modules, Pascal demonstrated an astounding level of dedication and a strong desire to learn. 
He consistently contributed to group discussions with thoughtful questions, often sparking engaging conversations that elevated the learning experience for everyone involved. 
His ability to listen actively, provide insightful feedback, 
and work collaboratively with his peers created a supportive and dynamic group environment.
He consistently displayed a deep commitment to gaining not just a superficial understanding of the material but also a thorough grasp of the underlying fundamental concepts. 

His approach to learning, coupled with his excellent grades, makes him an ideal candidate for the Bachelor Program at CERN.

\vspace{.5cm}

Based on my experience with Pascal, I am wholeheartedly convinced that he has the ability to meet and overcome the tasks and challenges he will face during his bachelor thesis at CERN. 
I strongly recommend him for this position without reservation.

\vspace{1cm}

Sincerely, \\
Jonas Ollesch

\end{document}
